%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart{}
  \resumeSubheading{Gameramp}{}
  \resumeSubSubheading{Senior Software Engineer}{\mbox{Sept 2025 {--} Jan 2026}}
    \resumeItemListStart{}
      \resumeItem{Architected and deployed scalable backend systems in \textbf{Java} on \textbf{Kubernetes} for AI-powered data platforms.}
      \resumeItem{Designed a multi-stage agentic pipeline (Triage, Text2SQL, Execution) enabling natural language querying over structured databases.}
      \resumeItem{Built an LLM-based evaluation setup using test suites to validate prompt changes and detect regressions in response quality.}
    \resumeItemListEnd{}

  \resumeSubheading{AI Systems Consulting}{}
  \resumeSubSubheading{Senior Software Engineer (Contract)}{\mbox{June 2025 {--} Sept 2025}}
    \resumeItemListStart{}
      \resumeItem{Architected agentic systems for enterprise clients, enabling scalable LLM-powered workflows across knowledge bases.}
      \resumeItem{Built orchestration pipelines (Triage, Planning, Execution) integrating \textbf{RAG} and enterprise MCP servers like ServiceNow and SAP.}
      \resumeItem{Developed scalable agent infrastructure in \textbf{Python} with CI/CD pipelines and \textbf{MCP registry} for integrating LLMs with external services.}
    \resumeItemListEnd{}

  \resumeSubheading{Plotline, Inc. (Founding Team)}{}
  \resumeSubSubheading{Software Engineer (SDE2 -> SDE3)}{\mbox{Apr 2022 {--} May 2025}}
  \resumeItemListStart{}
    \resumeItem{Led a team of 6 engineers from prototyping to production, establishing structured engineering processes across code reviews, hiring, onboarding, and mentorship.}
    \resumeItem{Built \textbf{CI/CD pipelines} with automated testing to improve release velocity, quality, and system reliability.}
    \resumeItem{Developed fullstack features using \textbf{React + TypeScript} for the dashboard and \textbf{Go} (core systems) + \textbf{Node.js + GraphQL} for APIs, handling peak load of \textbf{5M RPM} and \textbf{1B+ API calls daily}.}
    \resumeItem{Designed a Kafka-based event-driven segmentation system processing \textbf{10B+ events/day} for real-time user targeting.}
    \resumeItem{Built centralized logging, monitoring, and alerting infrastructure using \textbf{Datadog} and \textbf{Better Stack}, achieving a \textbf{99.9\% SLA}.}
    \resumeItem{Architected and supervised implementation of a multi-channel communication system delivering \textbf{5M+ messages/day} across Webhooks, Push, WhatsApp, Email, In-app overlays.}
  \resumeItemListEnd{}

  \resumeSubheading{Simply Vyapar Apps Pvt. Ltd.}{}
  \resumeSubSubheading{Software Engineer (SDE2)}{\mbox{Jun 2021 {--} Apr 2022}}
  \resumeItemListStart{}
    \resumeItem{Integrated Razorpay payments and built a reconciliation system using \textbf{Node.js}, resulting in a \textbf{20\%} reduction in transaction drop-offs and improved conversion rates in licensing process.}
    \resumeItem{Built a partner management platform with \textbf{React} dashboards and licensing workflows for internal and field partners, including automated distributor commission disbursement.}
    \resumeItem{Developed a bulk licensing automation pipeline enabling hourly onboarding of subscribers from a large B2B marketplace, eliminating manual processing and improving operational efficiency.}
  \resumeItemListEnd{}

  \resumeSubheading{Hyperverge, Inc.}{}
  \resumeSubSubheading{Software Engineer (SDE1)}{\mbox{Jun 2020 {--} Jun 2021}}
  \resumeItemListStart{}
    \resumeItem{Developed a cloud-agnostic identity verification and fraud detection stack using \textbf{Node.js} and \textbf{Python} for SEA nations.}
    \resumeItem{Transitioned core services to an asynchronous, event-driven architecture and set up performance monitoring and alerting system, reducing latency by \textbf{40\%}, achieving \textbf{99.999\% uptime} and maintaining \textbf{<0.01\% error rate}.}
    \resumeItem{Set up a Kubernetes-based job scheduling system for model training workloads, improving GPU utilization by \textbf{60\%}.}
  \resumeItemListEnd{}

  \resumeSubheading{Morningstar, Inc.}{}
  \resumeSubSubheading{Technology Intern}{\mbox{Jul 2019 {--} Dec 2019}}
  \resumeItemListStart{}
    \resumeItem{Implemented microservices to streamline ETL workflows enabling faster onboarding of new data sources.}
    \resumeItem{Developed an event-driven calculation engine for daily computation of financial indices for more than 400k securities.}
  \resumeItemListEnd{}
\resumeSubHeadingListEnd{}
