%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart{}
  \resumeSubheading{Exploring AI Systems}{}
  \resumeSubSubheading{Senior Software Engineer - Gameramp}{\mbox{Sept 2025 {--} Jan 2026}}
    \resumeItemListStart{}
      \resumeItem{Engineered scalable backend services and Kubernetes-based deployments for AI-powered data platforms.}
      \resumeItem{Architected a data pipeline (Triage -> Text2SQL -> Agentic analysis -> Execution) enabling conversational querying over databases.}
      \resumeItem{Developed an LLM-as-a-judge evaluation framework leveraging quorum-based validation and multi-agent debate to improve response reliability across production workflows.}
    \resumeItemListEnd{}
  \resumeSubSubheading{AI Consultant - Stealth Startup}{\mbox{June 2025 {--} Sept 2025}}{}
    \resumeItemListStart{}
      \resumeItem{Architected an agentic orchestration system (Triage -> Planner -> Execution) for interacting with enterprise knowledge bases.}
      \resumeItem{Built scalable agent infrastructure with CI/CD pipelines and an MCP registry for custom MCP servers integrating LLMs with services like ServiceNow, SAP, and Brave.}
      \resumeItem{Implemented semantic example retrieval using Qdrant vectorDB to improve agent accuracy and contextual relevance.}
    \resumeItemListEnd{}

  \resumeSubheading{Plotline, Inc. (Founding Team)}{}
  \resumeSubSubheading{Software Engineer (SDE2 -> SDE3)}{\mbox{Apr 2022 {--} May 2025}}
  \resumeItemListStart{}
    \resumeItem{Led a team of 6 engineers from prototyping to production, establishing structured engineering processes across code reviews, hiring, onboarding, and mentorship.}
    \resumeItem{Built \textbf{CI/CD pipelines} with automated testing to improve release velocity, quality, and system reliability.}
    \resumeItem{Developed a highly scalable Go server handling peak load of \textbf{5M RPM} and more than \textbf{1B+ API calls daily (P90: 0.4s, P99: 1s)}.}
    \resumeItem{Designed an event-driven segmentation system processing \textbf{10B+ events/day} for real time user targeting.}
    \resumeItem{Implemented centralized logging, monitoring and alerting mechanism with \textbf{Datadog} and \textbf{Better Stack}, enhancing system visibility and helping achieve a \textbf{99.9\%} SLA.}
    \resumeItem{Architected and supervised implementation of a multi-channel communication system delivering \textbf{5M+ messages/day} across Webhooks, Push, WhatsApp, Email, In-app overlays.}
  \resumeItemListEnd{}

  \resumeSubheading{Simply Vyapar Apps Pvt. Ltd.}{}
  \resumeSubSubheading{Software Engineer (SDE2)}{\mbox{Jun 2021 {--} Apr 2022}}
  \resumeItemListStart{}
    \resumeItem{Integrated Razorpay payments and built a reconciliation system, resulting in a \textbf{20\%} reduction in transaction drop-offs and improved conversion rates in licensing process.}
    \resumeItem{Built a partner management platform with dashboards and licensing workflows for internal and field partners, including automated distributor commission disbursement.}
    \resumeItem{Developed a bulk licensing automation pipeline enabling hourly onboarding of subscribers from a large B2B marketplace, eliminating manual processing and improving operational efficiency.}
  \resumeItemListEnd{}
    
  \resumeSubheading{Hyperverge, Inc.}{}
  \resumeSubSubheading{Software Engineer (SDE1)}{\mbox{Jun 2020 {--} Jun 2021}}
  \resumeItemListStart{}
    \resumeItem{Developed a cloud-agnostic identity verification and fraud detection stack for SEA nations.}
    \resumeItem{Transitioned core services to an asynchronous, event-driven architecture and set up performance monitoring and alerting system, reducing latency by \textbf{40\%}, achieving \textbf{99.999\% uptime} and maintaining \textbf{<0.01\% error rate}.}    
    \resumeItem{Set up a Kubernetes-based job scheduling system for model training workloads, improving GPU utilization by \textbf{60\%}.}
  \resumeItemListEnd{}

  \resumeSubheading{Morningstar, Inc.}{}
  \resumeSubSubheading{Technology Intern}{\mbox{Jul 2019 {--} Dec 2019}}
  \resumeItemListStart{}
    \resumeItem{Implemented microservices to streamline ETL workflows enabling faster onboarding of new data sources.}
    \resumeItem{Developed an event-driven calculation engine for daily computation of financial indices for more than 400k securities.}
  \resumeItemListEnd{}
\resumeSubHeadingListEnd{}
